Crop adaptation through gene flow

### 2016-06-29 crop_adaptation_gene_flow_gj_outline.tex
Update crop_adaptation_gene_flow_gj_outline.tex

>>>>

\subsection*{Cotton}
wendel1989genetic:
bidirectinal gene flow between diploid species G. arboreum and G. herbaceum
independent domestication events of G. arboreum and G. herbaceum

The old-world A genome became part of the new-word genome in the polyploidization event; talk about this?

abdalla2001genetic:
Lots of interbreeding between cultivated lines of cotton, but what about wild relatives?

Cotton tolerates crosses quite well.

fryxell1979natural:
Introgression from domesticate to wild cottons is prevalent enough to threaten the continued existence of two wild species, G. darwinii and G. tomentosum.

wendel1990allozyme:
confirms the suggestions (based on morphology) of fryxell1979natural (for G. darwinii)
